---
title: "Billionaires"
author: "Fabian & Robin"
date: "31.12.2023"
output: html_document
---

This is the R project of Fabian and Robin. We decided to analyse data from billionaires.  
For that, we found a dataset on kaggle.com: https://www.kaggle.com/datasets/nelgiriyewithana/billionaires-statistics-dataset  
This dataset contains data from the 4th of april 2023 and is used for 'exploring the global landscape of success'.  

```{r}
# We used these libraries:
library(ggplot2) # to plot graphs and images
```

# Read the CSV file into a dataframe called df_billionaires

```{r}
df_billionaires <- read.csv("BillionairesStatisticsDataset.csv")
# display data
head(df_billionaires)
```

# First inspection of the data

Each row displays one person that is a billionaire. The columns contain the following  
details about each person:  
  
- rank
  - The ranking of the billionaire in terms of wealth (from 1 to 2640).  
- finalWorth
  - The final net worth of the billionaire in U.S. dollars.  
- category
  - The category or industry in which the billionaire's business operates.  
- personName
  - The full name of the billionaire.  
- age
  - The age of the billionaire in years.  
- country
  - The country in which the billionaire resides.  
- city
  - The city in which the billionaire resides  
- source
  - The source of the billionaire's wealth (eg. company name).  
- industries
  - The industries associated with the billionaire's business interests.  
- countryOfCitizenship
  - The country of citizenship of the billionaire.  
- organization
  - The name of the organization or company associated with the billionaire.  
- selfMade
  - Indicates whether the billionaire is self-made (True/False).  
- status
  - D=Entrepreneur and U = Inherited  
- gender
  - The gender of the billionaire.  
- birthDate
  - The birthdate of the billionaire.  
- lastName
  - The last name of the billionaire.  
- firstName
  - The first name of the billionaire.  
- title
  - The status or position of the billionaire (e.g., CEO, Founder).  
- date
  - The date of data collection.  
- state
  - The state in which the billionaire resides.  
- redidenceStateRegion
  - The region or state of residence of the billionaire.  
- birthYear
  - The birth year of the billionaire.  
- birthMonth
  - The birth month of the billionaire.  
- birthDay
  - The birth day of the billionaire.  
- cpi_country
  - Consumer Price Index (CPI) for the billionaire's country.  
- cpi_change_country
  - CPI change for the billionaire's country.  
- gdp_country
  - Gross Domestic Product (GDP) for the billionaire's country.  
- gross_tertiary_education_enrollment
  - Enrollment in tertiary education in the billionaire's country.  
- gross_primary_education_enrollment_country
  - Enrollment in primary education in the billionaire's country.  
- life_expectancy_country
  - Life expectancy in the billionaire's country.  
- tax_revenue_country_country
  - Tax revenue in the billionaire's country.  
- total_tax_rate_country
  - Total tax rate in the billionaire's country.  
- population_country
  - Population of the billionaire's country.  
- latitude_country
  - Latitude coordinate of the billionaire's country.  
- longitude_country
  - Longitude coordinate of the billionaire's country.  

# We first started by creating a list of the top 10 richest billionaires:

```{r}
# Create a data frame with the top 10 billionaires
top_10_billionaires <- df_billionaires[1:10, ]
```

## Plot the top 10 richest billionaires
```{r}
# Create a bar plot with text labels
plot <- ggplot(top_10_billionaires, aes(x = reorder(personName, -finalWorth), y = finalWorth, fill = personName)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0("$", finalWorth, "B")), vjust = -0.5, color = "black", size = 3) + # Add text labels
  labs(
    title = "Top 10 Billionaires and their Net Worth",
    x = "Billionaires",
    y = "Net Worth (in billions USD)",
    fill = "Billionaire"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Print the plot
print(plot)
```
  
The plot displays ten bars in a barchart. Each bar represents the wealth of
one billionaire. The bar only displays the top 10 richest billionaires.
The height of the bar represents the wealth of the billionaire in US-dollars.

# Next Steps

Next, we decided to formulate a thesis. Based on the dataset, we decided that we want
to formulate our thesis about the correlation and causation between certain data
columns and the wealth of the billionaires. Maybe this lets us speculate on certain
circumstances that make it easier or harder for someone to become a billionaire.

In the following we will create multiple plots to compare the correlation between certain
data columns and the wealth. Because this dataset only contains billionaires, we won't
focus on the difference between their wealth. Being part of this dataset is rich enough ;

# Ideas
ICH HÄTTE ULTRA BOCK EIN PLOT ZU ERSTELLEN; INDEM ICH DEN WOHNORT AUF EINER WELTKARTE ALS
PLOT DARSTELLE. ALSO IRGENDWAS MIT MAP. (falls es dir nichts ausmacht.)