---
title: "Billionaires"
author: "Fabian & Robin"
date: "15.01.2024"
output: html_document
---
```{r setup, echo=FALSE, include=FALSE}
# Disable linting for file
# nolint start

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```

This is the R project of Fabian and Robin. We decided to analyse data from billionaires.  
For that, we found a dataset on kaggle.com: <https://www.kaggle.com/datasets/nelgiriyewithana/billionaires-statistics-dataset>  
This dataset contains data from the 4th of april 2023 and is used for 'exploring the global landscape of success'.  

In the following, we will create several graphs to compare the correlation between certain columns of data and wealth. As this dataset only contains billionaires, we won't focus on the difference between their wealth. Being part of this list already means being incredibly rich. Accordingly, it is not necessary to analyze how much wealth is considered rich.

# 1. Definition and formulation of the questions

## What interests you about the data set? (Our theses)

- The distribution of billionaire wealth is highly concentrated among a small number of individuals.
- There is a strong correlation between the industries in which billionaires make their fortunes and the overall GDP of their countries.
- The geographic distribution of billionaires across countries reflects the global economic landscape and the opportunities for wealth creation in different regions.
- The relationship between age and becoming a billionaire.
- Countries with lower tax rates have more billionaires.
- Countries with better educational attainment have more billionaires.

## What specific questions would you like to answer with the help of the data set?

- How many billionaires own more than 80% of the total wealth?
- Which industry is the most profitable?
- What is the relationship between the distribution of billionaire wealth and the economic strength of a country, measured by GDP, tax revenue and population?
- Is there a geographical pattern to the distribution of billionaires across countries?
  - If so, what factors contribute to this distribution?
- How many billionaires are self-made, and are younger billionaires more likely to be self-made?
- In which countries do most billionaires inherit their wealth and why?
- Which countries have the lowest tax rates and how many billionaires do they have?
- Is there a correlation between educational attainment and the number of billionaires in a country?

## What do you expect from the data set in view of your question?

- Most wealth is held by 10% of billionaires.
- The most profitable sector is technology.
- Modern economies have more self-made billionaires.
- There is no geographical pattern.
- Younger billionaires are more likely to be self-made.
- Location does not correlate with wealth.

# 2. Loading the data

Load the data into the R session and get an initial overview Which types are included?

- Is it ensured that all data has the correct type?
- Does the data have any "oddities" that you need to deal with, such as differently coded NA's, multiple tables, ... etc.
- Depending on the data set, you can also load the data into a database and then access it in R.

Describe what you need to do before you can prepare and edit the data in the next section!


## Load Libraries
```{r}
# We used these libraries:
library(ggplot2) # to plot graphs and images
library(dplyr)
library(ggcorrplot)
library(ggthemes)
library(tidyverse)
library(gridExtra)
library(plotly)
```

## Read the CSV file into a dataframe called df_billionaires

```{r}
df_billionaires <- read.csv("BillionairesStatisticsDataset.csv")
# display data
head(df_billionaires)
```

## First inspection of the data

Each row displays one person that is a billionaire. The columns contain the following\
details about each person:

-   rank
    -   The ranking of the billionaire in terms of wealth (from 1 to 2640).\
-   finalWorth
    -   The final net worth of the billionaire in U.S. dollars.\
-   category
    -   The category or industry in which the billionaire's business operates.\
-   personName
    -   The full name of the billionaire.\
-   age
    -   The age of the billionaire in years.\
-   country
    -   The country in which the billionaire resides.\
-   city
    -   The city in which the billionaire resides\
-   source
    -   The source of the billionaire's wealth (eg. company name).\
-   industries
    -   The industries associated with the billionaire's business interests.\
-   countryOfCitizenship
    -   The country of citizenship of the billionaire.\
-   organization
    -   The name of the organization or company associated with the billionaire.\
-   selfMade
    -   Indicates whether the billionaire is self-made (True/False).\
-   status
    -   D=Entrepreneur and U = Inherited\
-   gender
    -   The gender of the billionaire.\
-   birthDate
    -   The birthdate of the billionaire.\
-   lastName
    -   The last name of the billionaire.\
-   firstName
    -   The first name of the billionaire.\
-   title
    -   The status or position of the billionaire (e.g., CEO, Founder).\
-   date
    -   The date of data collection.\
-   state
    -   The state in which the billionaire resides.\
-   redidenceStateRegion
    -   The region or state of residence of the billionaire.\
-   birthYear
    -   The birth year of the billionaire.\
-   birthMonth
    -   The birth month of the billionaire.\
-   birthDay
    -   The birth day of the billionaire.\
-   cpi_country
    -   Consumer Price Index (CPI) for the billionaire's country.\
-   cpi_change_country
    -   CPI change for the billionaire's country.\
-   gdp_country
    -   Gross Domestic Product (GDP) for the billionaire's country.\
-   gross_tertiary_education_enrollment
    -   Enrollment in tertiary education in the billionaire's country.\
-   gross_primary_education_enrollment_country
    -   Enrollment in primary education in the billionaire's country.\
-   life_expectancy_country
    -   Life expectancy in the billionaire's country.\
-   tax_revenue_country_country
    -   Tax revenue in the billionaire's country.\
-   total_tax_rate_country
    -   Total tax rate in the billionaire's country.\
-   population_country
    -   Population of the billionaire's country.\
-   latitude_country
    -   Latitude coordinate of the billionaire's country.\
-   longitude_country
    -   Longitude coordinate of the billionaire's country.

## We first started by creating a list of the top 10 richest billionaires:
```{r}
# Create a data frame with the top 10 billionaires
df_temp <- df_billionaires[1:10, ]

# Create a bar plot with text labels
ggplot(df_temp, aes(x = reorder(personName, -finalWorth), y = finalWorth, fill = personName)) + # nolint: line_length_linter, line_length_linter.
    geom_bar(stat = "identity") +
    geom_text(aes(label = paste0("$", finalWorth, "B")), vjust = -0.5, color = "black", size = 3) + # Add text labels # nolint: line_length_linter.
    labs(
        title = "Top 10 Billionaires and their Net Worth",
        x = "Billionaires",
        y = "Net Worth (in billions USD)",
        fill = "Billionaire"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

The plot displays ten bars in a barchart. Each bar represents the wealth of one billionaire. The plot only displays the top 10 richest billionaires. The height of the bar represents the wealth of the billionaire in US-dollars.

## correlation matrix between numeric values

The code calculates and visualizes the correlation matrix of numeric variables in the dataset, indicating the strength and direction of linear relationships between measures such as wealth, age, Consumer Price Index, Gross Domestic Product, life expectancy, and other relevant numeric columns.

```{r}
df_temp <- df_billionaires
# Convert 'birthDate' to Date type
df_temp$birthDate <- as.Date(df_temp$birthDate, format = "%m/%d/%Y")

# Filter only numeric columns for correlation analysis
numeric_cols <- sapply(df_temp, is.numeric)
df_temp_numeric <- df_temp[, numeric_cols]

# Remove column rank
df_temp_numeric <- df_temp_numeric[, !colnames(df_temp_numeric) %in% c("rank")]

# Remove NA and NaN values
df_temp_numeric <- na.omit(df_temp_numeric)

# Plot correlation matrix
ggcorrplot(cor(df_temp_numeric), type = "lower", lab = TRUE)
```
As you can see... 
TODO: CHANGE SIZE OF PLOT TO MAKE IT READABLE?

# 3. Editing/transforming the data

In this section, you should perform all the necessary transformations/cleansing/... etc. of the data (Data Muning, Data Cleansing), e.g:  

- Recoding of data, e.g. numerical to categorical
- Subsetting the data
- Joining of data tables - if necessary. Which join is necessary? Why?
- ...

Get an overview of the transformed data. You can use tools such as
`glimpse()`, `skim()` and `head()` to illustrate your explanations.  
  
Is the resulting data what you expected? Why or why not?

## The distribution of billionaire wealth is highly concentrated among a small number of individuals.

## There is a strong correlation between the industries in which billionaires make their fortunes and the overall GDP of their countries.

```{r}
# Clean 'finalWorth' column and convert to numeric
df_billionaires$finalWorth <- as.numeric(gsub("[^0-9.]", "", df_billionaires$finalWorth))
```

## The geographic distribution of billionaires across countries reflects the global economic landscape and the opportunities for wealth creation in different regions.

## The relationship between age and becoming a billionaire.

## Countries with lower tax rates have more billionaires.

## Countries with better educational attainment have more billionaires.

## Remaining questions

# 4. Appropriate visualization and aggregation of the data

Summarize the data in a suitable form to answer your formulated question.
summarized. You should also use suitable visualizations of the transformed and/or aggregated data
to support or illustrate your statements accordingly.  

You can also use suitable statistical methods or modeling here if they help you with your research question.

## The distribution of billionaire wealth is highly concentrated among a small number of individuals.

We think that only a small amount of individuals own a huge part of the entire wealth of all billionaires. The same is already proven for the entire world population: "half of the world's net wealth belongs to the top 1%, top 10% of adults hold 85%, while the bottom 90% hold the remaining 15% of the world's total wealth, top 30% of adults hold 97% of the total wealth". 

For that, we'll look at the wealth distribution between the billionaires in this dataset:

```{r}
ggplot(df_billionaires, aes(x = finalWorth)) +
    geom_histogram(binwidth = 10000, fill = "blue", color = "black") +
    labs(title = "Billionaire Wealth Distribution", x = "Final Worth", y = "Amount of billionaires") +
    theme_minimal()
```

The plot shows, that the lower the finalWorth is, the higher the frequency gets. This means that most billionaires are barely above the threshold of 1 billion usd. Only a few billionaires have a higher finalWorth than 25000 million usd.

### How many billionaires own more than 80% of the total wealth?

Due to the global wealth being around $454.4 trillion in 2022. We cannot really calculate the amount of people that own 80% of the global wealth. But we can calculate the amount of billionaires that own more than 80% of the totalWealth of all billionaires:

```{r}
# Calculate the total wealth
total_wealth <- sum(df_billionaires$finalWorth)

cat("All billionaires wealth combined sums up to", total_wealth, "million usd.\n")

# Calculate percentage of billionaires wealth compared to global wealth:
result <- (total_wealth * 1e6) / (454.4 * 1e12)
cat("The entire wealth of all billionaires is just", result * 100, "% of the global wealth.\n")

# Sort billionaires by wealth in descending order
sorted_billionaires <- df_billionaires[order(df_billionaires$finalWorth, decreasing = TRUE), ]

# Calculate the cumulative sum of wealth
sorted_billionaires$cumulative_wealth <- cumsum(sorted_billionaires$finalWorth)

# Find the number of billionaires required to own more than 80% of total wealth
num_billionaires_80_percent <- sum(sorted_billionaires$cumulative_wealth <= 0.8 * total_wealth)

# Print the result
cat("Number of billionaires owning more than 80% of total wealth of billionaires:", num_billionaires_80_percent, "\n")
```

The richest 1157 billionaires own 80% of the combined wealth of all billionaires. Assuming this dataset is complete, there are 2640 billionaires.

Let's look at how many billionaires own half the entire wealth of all billionaires:

```{r}
# Find the number of billionaires required to own more than 80% of total wealth
num_billionaires_80_percent <- sum(sorted_billionaires$cumulative_wealth <= 0.5 * total_wealth)

# Print the result
cat("Number of billionaires owning more than 50% of total wealth of billionaires:", num_billionaires_80_percent, "\n")
```

Only 302 of all 2640 billionaires own more than 50% of the total wealth. This proves that the tendency stays the same for the richest interval of wealth (billionaires) compared to the entire scope. 

## There is a strong correlation between the industries in which billionaires make their fortunes and the overall GDP of their countries.

To check if there is a correlation, lets compare the industries with the gdp:

```{r}
ggplot(df_billionaires, aes(x = finalWorth, y = industries)) +
    geom_point() +
    labs(
        title = "Correlation Between GDP (finalWorth) and Industry",
        x = "GDP (finalWorth)",
        y = "Industry"
    )
```

On this plot you cannot really see a pattern. Lets zoom in on billionaires below $25 billion:

```{r}
# Filter the dataset for billionaires with wealth below $25,000
filtered_data <- subset(df_billionaires, finalWorth < 25000)

# Create a scatter plot
ggplot(filtered_data, aes(x = finalWorth, y = industries)) +
    geom_point() +
    labs(
        title = "Correlation Between GDP (finalWorth) and Industry for Billionaires Below $25,000",
        x = "GDP (finalWorth)",
        y = "Industry"
    )
```

There is no obvious pattern or correlation.

### Which industry is the most profitable?

To calculate the most profitable industry, we can calculate the average wealth for each industry and compare them:

```{r}
# Calculate average wealth by industry
average_wealth_by_industry <- tapply(df_billionaires$finalWorth, df_billionaires$industries, mean, na.rm = TRUE)

# Identify the industry with the highest average wealth
most_profitable_industry <- names(average_wealth_by_industry[which.max(average_wealth_by_industry)])

# Print the result
cat("The most profitable industry is:", most_profitable_industry, "\n")
```

```{r}
# Create a data frame for plotting
plot_data <- data.frame(
    industry = names(average_wealth_by_industry),
    average_wealth = average_wealth_by_industry
)

# Sort the data frame by average wealth
plot_data <- plot_data[order(plot_data$average_wealth, decreasing = TRUE), ]

# Bar plot
barplot(plot_data$average_wealth,
    names.arg = plot_data$industry,
    main = "Average Wealth by Industry",
    xlab = "Industry", ylab = "Average Wealth",
    col = "skyblue", cex.names = 0.8, las = 2
)
```

This bar chart shows that the industries don't really differ in being the most profitable. Also the results are inaccurate, due to vague classifications of their industries.

The following bar chart shows the wealth distribution over all industries given in the data set. It also differentiates between self-made wealth and inherited wealth. I also removed the top billionaires above $25 billion.

```{r}
# Bar chart: Wealth by Industry
ggplot(filtered_data, aes(x = reorder(category, -finalWorth), y = finalWorth, fill = selfMade)) +
    geom_bar(stat = "identity", position = "dodge") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(
        title = "Wealth by Industry",
        x = "Industry",
        y = "Final Net Worth",
        fill = "Self-Made"
    )
```

Billionaires working in Energy, Telecom, Gambling & Casinos, Sports, Service and Construction & Engineering are mostly self-made. Industries like Finance & Investment and Media & Entertainment are dominated by billionaires that inherited their wealth. Overall the Technology and Manufacturing industry has a lot of billionaires below $25 billion. We should also mention that this data is probably not 100% accurate due to the rough classification of the industry of each billionaire.

### What is the relationship between the distribution of billionaire wealth and the economic strength of a country, measured by GDP, tax revenue and population?

SAMPLE

```{r}

```

SAMPLE

## The geographic distribution of billionaires across countries reflects the global economic landscape and the opportunities for wealth creation in different regions.
### Is there a geographical pattern to the distribution of billionaires across countries?<br>If so, what factors contribute to this distribution?
Let's first examine the number of billionaires per country.
```{r}
# Filter for billionaires with country
df_temp <- na.omit(df_billionaires["country"]) %>%
    # Group by country
    group_by(country) %>%
    # Count billionaires per country
    summarise(count = n()) %>%
    # Sort by count
    arrange(desc(count))

# Plot as world map with plotly
plot_ly(
    type = "choropleth",
    locations = df_temp$country,
    locationmode = "country names",
    z = df_temp$count,
    text = df_temp$country,
    colorscale = "Turbo",
    colorbar = list(title = "Amount"),
) %>%
    layout(
        title = "Number of Billionaires per Country",
        geo = list(
            showframe = FALSE
        )
    )
```
The five countries with the most billionaires are:
```{r}
for (i in 1:5) {
    cat(df_temp[i, ]$country, ":", df_temp[i, ]$count, "\n")
}
```
What we can observe is that the highest number of billionaires resides in the USA, China, and India.\
This is unsurprising, given that these countries possess the highest economic power.\

Now, let's turn our attention to the total wealth of billionaires per country.
```{r}
# Get finalworth per country
df_temp <- na.omit(df_billionaires[c("country", "finalWorth")]) %>%
    # Group by country
    group_by(country) %>%
    # Count billionaires per country
    summarise(
        count = n(),
        total_finalWorth = (sum(finalWorth) / 1000)
        # Hier können Sie weitere Aggregationsfunktionen hinzufügen, falls benötigt
    ) %>%
    # Keep only countries with more than 4 billionaires
    filter(count >= 5)
# Plot as world map with plotly
plot_ly(
    type = "choropleth",
    locations = df_temp$country,
    locationmode = "country names",
    z = df_temp$total_finalWorth,
    text = df_temp$country,
    colorscale = "Turbo",
    colorbar = list(title = "Net Worth"),
) %>%
    layout(
        title = "Summed up wealth of billionaires per country in billion USD",
        geo = list(
            showframe = FALSE
        )
    )
```
This graph appears almost identical to the previous one. The most noteworthy observation is that the greatest wealth is concentrated in the USA and China. This might be attributed to the fact that the USA boasts the highest number of billionaires at 754, and China's economy has recently transformed from a predominantly agrarian and impoverished nation to the world's second-largest economy, fueled by market reforms and globalization.\

Next, we can gain an overview of the industries in which billionaires are involved per country. Perhaps we can identify a pattern where the industry is closely tied to the country.
```{r}
df_us <- na.omit(df_billionaires[c("country", "industries")]) %>%
    filter(country == "United States") %>%
    group_by(industries) %>%
    summarise(
        count = n()
    ) %>%
    arrange(desc(count))

df_china <- na.omit(df_billionaires[c("country", "industries")]) %>%
    filter(country == "China") %>%
    group_by(industries) %>%
    summarise(
        count = n()
    ) %>%
    arrange(desc(count))

df_india <- na.omit(df_billionaires[c("country", "industries")]) %>%
    filter(country == "India") %>%
    group_by(industries) %>%
    summarise(
        count = n()
    ) %>%
    arrange(desc(count))
```
Let's begin by examining the industries in the USA.
```{r}
ggplot(df_us[1:10, ], aes(x = reorder(industries, -count), y = count)) +
    geom_bar(stat = "identity") +
    labs(
        title = "US industries",
        x = "Industry",
        y = "Amount"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
The majority of billionaires in the US are in the finance and investment industry, followed by the technology and food & beverage industry.
```{r}
ggplot(df_china[1:10, ], aes(x = reorder(industries, -count), y = count)) +
    geom_bar(stat = "identity") +
    labs(
        title = "Chinese industries",
        x = "Industry",
        y = "Amount"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
In China, the most billionaires are in the manufacturing industry, followed by the technology and healthcare industry.
```{r}
ggplot(df_india[1:10, ], aes(x = reorder(industries, -count), y = count)) +
    geom_bar(stat = "identity") +
    labs(
        title = "Indian industries",
        x = "Industry",
        y = "Amount"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Like in China, the majority of billionaires in India are in the manufacturing industry. The second-largest group of billionaires in India is in the healthcare sector.\

If we delve into the manufacturing industry in both China and India, we discover that China holds the title of the world's largest manufacturing economy and exporter of goods, as mentioned earlier. India's manufacturing industry has been experiencing rapid growth in recent years. This growth can be attributed to the comparatively low labor costs in both India and China.\

However, previous analyses of GDP and industrial sectors have shown that there is no correlation between the sector/GDP and being a billionaire.\

The only potentially existing geographical connection is that approximately 18% of the world's population resides in both China and India. This is the only pattern that could explain the distribution of billionaires across these countries, suggesting that where more people live, there is also a greater potential for individuals to become billionaires.\

### In which countries do most billionaires inherit their wealth and why?
```{r}
df_temp <- filter(df_billionaires[c("country", "selfMade")], country != "") %>%
    na.omit() %>%
    group_by(country, selfMade) %>%
    summarise(count = n()) %>%
    arrange(selfMade, desc(count))

# delete all entries which are not in the list of top 10 inherited countries
df_temp <- df_temp[df_temp$country %in% df_temp[1:10, ]$country, ] %>%
    arrange(country, desc(count))

# Plot a bar chart of the top 10 countries with the most inherited billionaires.
# Also showing the total amount of billionaires per country. (2 bars in one chart)
ggplot(df_temp, aes(x = country, y = count, fill = factor(selfMade))) +
    geom_bar(stat = "identity", position = position_dodge()) +
    geom_text(aes(label = count), position = position_dodge(width = 0.9), vjust = -0.5) +
    labs(
        title = "Billionaires Count by Country and SelfMade Status",
        x = "Country",
        y = "Count",
        fill = "SelfMade"
    ) +
    theme_minimal()
```
The country with the most billionaires also tops the list for inherited billionaires, reflecting a correlation between a higher billionaire count and inheritance opportunities. China, ranking second in billionaires globally, exhibits the lowest number of inherited billionaires on the graph, indicating a distinctive wealth distribution pattern. This could be due to fast economic changes and the socialist influences discouraging wealth inheritance.

To check further why billionaires inherit their wealth, we examine if there is a mathematical correlation between the 'self-made' attribute and other attributes.
```{r}
# use df_billionaires and corellate selfMade with some columns
columns <- c("gender", "category", "birthYear", "birthMonth", "age", "finalWorth", "country", "city", "state", "selfMade")

df_temp <- na.omit(df_billionaires[columns])

# convert columns to factor
df_temp <- as.data.frame(lapply(df_temp, as.factor))

# conver all to numeric
df_temp <- as.data.frame(lapply(df_temp, as.numeric))

# corellate selfMade attribute with everything
self_made_corr <- cor(df_temp)

# Print out the correlations of selfMade
self_made_corr <- self_made_corr["selfMade", ]

# Drop selfMade
self_made_corr <- self_made_corr[-which(names(self_made_corr) == "selfMade")]

# print temp as bar chart (temp is named vector)
ggplot(data.frame(x = names(self_made_corr), y = self_made_corr), aes(x = reorder(x, -y), y = y)) +
    geom_bar(stat = "identity") +
    labs(
        title = "correlation of Self-Made with other Attributes",
        x = "Attribute",
        y = "correlation"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
print(self_made_corr)
```
The highest existing correlation is between gender and the self-made status, with a value of 0.32. However, this is likely because it was historically more challenging for women to establish businesses and accumulate wealth.\

The second-highest value is the linear correlation between income category and the self-made status, with a value of 0.19. Both of these mentioned values, however, are too low to truly confirm a correlation between the attributes. This holds true for the other attributes in the graph as well.

## The relationship between age and becoming a billionaire.
This plot gives on overview on the generated or inherited wealth by each billionaire indexed by their age. The x-axis demonstrates the age from 1 to 100+ and the y-axis demonstrates the wealth. Blue dots indicate a self-made wealth, while red dots indicate inherited wealth.

```{r}
# Scatter plot: Wealth vs. Age
ggplot(df_billionaires, aes(x = age, y = finalWorth, color = selfMade)) +
    geom_point() +
    labs(
        title = "Wealth vs. Age",
        x = "Age",
        y = "Final Net Worth",
        color = "Self-Made"
    )
```

Let's also look at the youngest self-made billionaire:

```{r}
df_temp <- df_billionaires
# Remove NA values
df_temp <- na.omit(df_temp)
# Filter for self-made billionaires and find the minimum age
youngest_age <- min(df_temp[df_temp$selfMade == TRUE, ]$age)
# Print the result
cat("The age of the youngest self-made billionaire is", youngest_age, "years.")
```

This indicates that young billionaires below the age of 28 most definitely inherited their wealth. The youngest self-made billionaire is 28 years old. As the age increases, there is no obvious pattern. The only thing worth mentioning is that the richest billionaires are mostly self-made. This probably results out of the fact of inflation and the growing gap between rich and poor.
Let's zoom in on billionaires with a wealth below $25 billion:

```{r}
# Filter out rows with missing values in finalWorth or age
filtered_data <- subset(df_billionaires, !is.na(finalWorth) & !is.na(age) & finalWorth < 25000)

# Scatter plot: Wealth vs. Age
ggplot(filtered_data, aes(x = age, y = finalWorth, color = selfMade)) +
    geom_point() +
    labs(
        title = "Wealth vs. Age",
        x = "Age",
        y = "Final Net Worth",
        color = "Self-Made"
    )
```

This also shows no obvious pattern. 

Let's also look at a bar chart showing the amount of billionaires for each age:

```{r}
# Create a bar plot: Count of billionaires by age, differentiated by selfMade
ggplot(filtered_data, aes(x = age, fill = factor(selfMade))) +
    geom_bar(position = "dodge", color = "black") +
    labs(
        title = "Number of Billionaires by Age",
        x = "Age",
        y = "Number of Billionaires",
        fill = "Self-Made"
    ) +
    theme_minimal()
```

Here you can see that self-made billionaires are generally younger than billionaires who inherited their wealth. You can also see a lot of self-made billionaires who are about 58 years old. This may indicate that being born about 60 years ago is a good time to get rich.

### How many billionaires are self-made, and are younger billionaires more likely to be self-made?

First let's look at how many billionaires are self-made:

```{r}
# Count the number of self-made billionaires
self_made_count <- sum(df_billionaires$selfMade == TRUE)

# Print the count
cat("Number of self-made billionaires: ", self_made_count, "/2640\n")
```

Out of the 2,640 billionaires worldwide, 1,812 are considered self-made, meaning they accumulated their wealth through entrepreneurship and business endeavors rather than inheriting it. This trend can be attributed to the increasing opportunities for innovation and entrepreneurship in the global economy, fostering a conducive environment for individuals to create and grow their own businesses. Factors such as technological advancements, globalization, and access to capital have empowered individuals to pursue entrepreneurial ventures, leading to a significant number of self-made billionaires. Additionally, the rise of industries like technology has provided platforms for innovative minds to disrupt traditional business models and amass substantial fortunes.
Are younger billionaires more likely to be self-made?

```{r}
# Create age groups (you can adjust the breaks and labels accordingly)
age_breaks <- c(0, 20, 30, 40, 50, 60, 70, 80, 90, Inf)
age_labels <- c("<20", "20-29", "30-39", "40-49", "50-59", "60-69", "70-79", "80-89", "90+")
df_billionaires$age_group <- cut(df_billionaires$age, breaks = age_breaks, labels = age_labels, right = FALSE)

# Create a summary table of the proportion of self-made billionaires in each age group
summary_table <- table(df_billionaires$age_group, df_billionaires$selfMade)
prop_table <- prop.table(summary_table, margin = 1)

# Create a bar plot
ggplot(df_billionaires, aes(x = age_group, fill = factor(selfMade))) +
    geom_bar(position = "fill") +
    labs(
        title = "Proportion of Self-Made Billionaires in Different Age Groups",
        x = "Age Group",
        y = "Proportion"
    ) +
    scale_fill_manual(values = c("FALSE" = "red", "TRUE" = "green"), name = "Self-Made")
```

No, young billionaires are not more likely to be self-made. Between the age of 30 and 90, most billionaires are self-made.

## Countries with lower tax rates have more billionaires.
### Which countries have the lowest tax rates and how many billionaires do they have?
First of all we wanted to find out which countries have the lowest tax rates.\
We also take a look at the countries with the highest tax rates to compare these with each other.
```{r}
# Get the countries with the lowest tax rates
lowest_tax <- df_billionaires[c("total_tax_rate_country", "country")] %>%
    # Remove NA values
    na.omit() %>%
    # Group by country
    group_by(country) %>%
    # Count billionaires per country
    summarise(
        total_tax_rate_country = first(total_tax_rate_country),
        count = n()
    ) %>%
    # Filter Argentina, because tax rate of 106,3% is not realistic.
    filter(country != "Argentina") %>%
    # Sort by total_tax_rate_country
    arrange(total_tax_rate_country)

# plot barchart for the top 10 countries with the lowest tax rate
plot1 <- ggplot(lowest_tax[1:15, ], aes(x = reorder(country, total_tax_rate_country), y = total_tax_rate_country)) +
    geom_bar(stat = "identity") +
    labs(
        title = "Top 10 countries with the lowest tax rate",
        x = "Country",
        y = "Tax Rate"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

# plot the amount of billionaires for the top 10 countries with the lowest tax rate
plot2 <- ggplot(lowest_tax[1:15, ], aes(x = reorder(country, total_tax_rate_country), y = count)) +
    geom_bar(stat = "identity") +
    labs(
        title = "Top 10 countries with the lowest tax rate",
        x = "Country",
        y = "Count"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

highest_tax <- arrange(lowest_tax, desc(total_tax_rate_country))

# plot barchart for the top 10 countries with the highest tax rate
plot3 <- ggplot(highest_tax[1:15, ], aes(x = reorder(country, -total_tax_rate_country), y = total_tax_rate_country)) +
    geom_bar(stat = "identity") +
    labs(
        title = "Top 10 countries with the highest tax rate",
        x = "Country",
        y = "Tax Rate"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

# plot the amount of billionaires for the top 10 countries with the highest tax rate
plot4 <- ggplot(highest_tax[1:15, ], aes(x = reorder(country, -total_tax_rate_country), y = count)) +
    geom_bar(stat = "identity") +
    labs(
        title = "Top 10 countries with the highest tax rate",
        x = "Country",
        y = "Count"
    ) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

grid.arrange(plot1, plot2, plot3, plot4, ncol = 2)
```
Georgia has the lowest tax rate at 9.9%. There is only one billionaire in Georgia. The first graph depicts a total of 155 billionaires.
The country with the highest tax rate is Colombia, with a rate of 71.2%. Colombia also has only one billionaire. The second graph shows a total of 1019 billionaires.\

When comparing these plots, we can observe that more billionaires live in countries with higher tax rates.
In this plot, it is notably influenced by China; however, even when excluding China from consideration, the graph with higher tax rates still accumulates more billionaires than the one with lower tax rates.\

This observation, though, is not representative enough to make a statement about whether countries with higher tax rates have more billionaires. Further studies would be needed to draw a conclusive conclusion.

## Countries with better educational attainment have more billionaires.
Let us first get an overview of the amount of billionaires .\
```{r}
# Get the countries with the best educational attainment
df_education <- df_billionaires[c("gross_primary_education_enrollment_country", "gross_tertiary_education_enrollment", "country")] %>%
    # Remove NA values
    na.omit() %>%
    # Group by country
    group_by(country) %>%
    # Count billionaires per country
    summarise(
        primary_education = first(gross_primary_education_enrollment_country),
        tertiary_education = first(gross_tertiary_education_enrollment),
        count = n()
        # Hier können Sie weitere Aggregationsfunktionen hinzufügen, falls benötigt
    ) %>%
    arrange(desc(primary_education))

df_temp_primary <- df_education
df_temp_tertiary <- arrange(df_education, desc(tertiary_education))
```
```{r}
# print the amount of billionaires of the first five countries with the best primary education
{
    cat("Amount of billionaires in the first five countries with the best primary education:\n")
    for (i in 1:5) {
        cat(df_temp_primary[i, ]$country, ":", df_temp_primary[i, ]$count, "\n")
    }
}
# print the amount of billionaires of the first five countries with the best tertiary education
{
    cat("Amount of billionaires in the first five countries with the best tertiary education:\n")
    for (i in 1:5) {
        cat(df_temp_tertiary[i, ]$country, ":", df_temp_tertiary[i, ]$count, "\n")
    }
}
```
Lets do the same for the countries with the lowest educational attainment:
```{r}
{
    lowest_primary <- arrange(df_temp_primary, primary_education)
    cat("Amount of billionaires in the first five countries with the lowest primary educational enrollment:\n")
    for (i in 1:5) {
        cat(lowest_primary[i, ]$country, ":", lowest_primary[i, ]$count, "\n")
    }
}
# print the amount of billionaires of the first five countries with the best tertiary education
{
    lowest_tertiary <- arrange(df_temp_tertiary, tertiary_education)
    cat("Amount of billionaires in the first five countries with the lowest tertiary educational enrollment:\n")
    for (i in 1:5) {
        cat(lowest_tertiary[i, ]$country, ":", lowest_tertiary[i, ]$count, "\n")
    }
}
```
If we compare those we can clearly see, that there are more billionaires in countries with better educational attainment.\
This could be an indicator that the educational attainment is a factor for becoming a billionaire.\ 

### Is there a correlation between educational attainment and the number of billionaires in a country?

Now lets calculate if there is a correlation between the amount of billionaires and the primary/tertiary education.\
```{r}
education_corr_df <- df_education
# convert columns to factor
education_corr_df <- as.data.frame(lapply(education_corr_df, as.factor))

# conver all to numeric
education_corr_df <- as.data.frame(lapply(education_corr_df, as.numeric))

# calculate correlation between count of billionaires and primary/tertiary education
education_corr <- cor(education_corr_df)

# print correlation for primary and secondary education
{
    cat("Correlation: billionaires - primary education:", education_corr["count", "primary_education"], "\n")
    cat("Correlation: billionaires - tertiary education:", education_corr["count", "tertiary_education"], "\n")
}
```
The correlation between the number of billionaires and primary education is 0.035 (3.5%). The correlation for tertiary education is 0.249 (24.9%).\

From this, we can deduce that there is no connection between primary education and the number of billionaires.\
However, tertiary education shows a slight linear relationship with the number of billionaires.\
This could make sense since tertiary education represents the highest level of education.

# 5. Summary and conclusion
Summarize your research question and your findings from your analysis here.  
Are your findings what you expected? Why or why not?
